FEM Model Analysis

### 2021-09-13 FEM_R/model_analysis_core.Rmd
Modified the model_analysis_core.Rmd script to include the T-test table for continuous economic variables (wealth and income)

```{r include=FALSE}
# Set up vector with all p-value column names. Require these for table formatting
pValNames <- c('P_Value_3', 'P_Value_4', 'P_Value_5', 'P_Value_6', 'P_Value_7', 'P_Value_8')
```

@@

```{r echo = FALSE}
## This block will define the logic for creating the tables with Reactable
# The tables are formatted exaclty the same for each group of vars so makes sense to define this only once

@@

### Binary Health
```{r echo = FALSE}
# Create the actual table!
binhlthTab <- createTTT(binhlth)
binhlthTab
```
### Binary Economic
```{r echo = FALSE}
# Create the actual table!
bineconTab <- createTTT(binecon)
bineconTab
```
### Risk Behaviours
```{r echo = FALSE}
# Create the actual table!
riskTab <- createTTT(risk)
riskTab
```

# Cross Validation 2 - 'Handover' plots (Still WIP need fixing)

```{r echo = FALSE}
vis_CV2_prev <- function(long, CV2) {

  # Keep only waves 1 - 4
  longC <- subset(long, wave < 5)
  longC <- as.data.table(longC)

  # Replace all NA with 0
  longC[is.na(longC)] <- 0

  # Have to drop r*clust vars as they contain strings
  longC <- select(longC, -contains('clust'))

  # Now get the weighted mean by wave of every column based on cwtresp
  l2 <- longC[ , lapply(.SD,weighted.mean,w=cwtresp), by = list(wave)]

  # ELSA_long is now processed to the point where we can start extracting and combining variables
  # Better start by adding year to l2 and reordering the columns
  l2$year <- seq(from=2002, to = 2008, by = 2)
  setcolorder(l2, c('year', 'wave'))

  # Now lets extract chronic disease variables from both dataframes and do a row combine
  # Start with cancre, diabe, hearte
  cd_l2 <- select(l2, c(year, age, cancre, diabe, hearte, lunge, smoken, bmi, employed, anyadl)) #, anyiadl, adl1, adl2, adl3p))
  cd_CV2 <- select(CV2, c(year, a_age_all, p_cancre_all, p_diabe_all, 
                            p_hearte_all, p_lunge_all, p_smoken_all, 
                            a_bmi_all, p_employed_all,  p_anyadl_all))
                            #, p_anyiadl_all p_adl1_all, p_adl2_all, p_adl3p_all))

  CV2_rename <- cd_CV2 %>% dplyr::rename('age' = a_age_all,
                                        'cancre' = p_cancre_all, 
                                        'diabe' = p_diabe_all, 
                                        'hearte' = p_hearte_all,
                                        'lunge' = p_lunge_all,
                                        'smoken' = p_smoken_all,
                                        'bmi' = a_bmi_all,
                                        'employed' = p_employed_all,
                                        'anyadl' = p_anyadl_all)
                                        #'anyiadl' = p_anyiadl_all)
                                        #'adl1' = p_adl1_all,
                                        #'adl2' = p_adl2_all,
                                        #'adl3p' = p_adl3p_all)

  combine <- rbind(cd_l2, CV2_rename)

  melted <- reshape2::melt(combine, id.var = 'year', value.name = 'Prevalence')

  ggplot(data = melted, aes(x = year, y = Prevalence, color = variable)) +
          geom_line() +
          facet_wrap(. ~ variable, scales = "free")
          #theme(panel.spacing.x = unit(1.5, 'lines')) +
          #labs(title = 'Prevalence of Chronic Disease', x = 'Year', y = 'Prevalence')
}

# Load in whole stock pop, plus the CV2 summary output file
long <- read_dta('../../input_data/ELSA_long.dta')
CV2 <- read_dta('ELSA_CV2/ELSA_CV2_summary.dta')

vis_CV2_prev(long, CV2)
```

Second go at this cross-validation, attempting to solve some issues by using the 60 plus population.

```{r echo = FALSE}
vis_CV2_prev <- function(long, CV2) {

  # Keep only waves 1 - 4
  longC <- subset(long, wave < 5)
  longC <- as.data.table(longC)

  # Replace all NA with 0
  longC[is.na(longC)] <- 0

  # Have to drop r*clust vars as they contain strings
  longC <- select(longC, -contains('clust'))

  # Now get the weighted mean by wave of every column based on cwtresp
  l2 <- longC[ , lapply(.SD,weighted.mean,w=cwtresp), by = list(wave)]

  # ELSA_long is now processed to the point where we can start extracting and combining variables
  # Better start by adding year to l2 and reordering the columns
  l2$year <- seq(from=2002, to = 2008, by = 2)
  setcolorder(l2, c('year', 'wave'))

  # Now lets extract chronic disease variables from both dataframes and do a row combine
  # Start with cancre, diabe, hearte
  cd_l2 <- select(l2, c(year, age, cancre, diabe, hearte, lunge, smoken, bmi, employed, anyadl)) #, anyiadl, adl1, adl2, adl3p))
  cd_CV2 <- select(CV2, c(year, a_age_60p, p_cancre_60p, p_diabe_60p, 
                            p_hearte_60p, p_lunge_60p, p_smoken_60p, 
                            a_bmi_60p, p_employed_60p,  p_anyadl_60p))
                            #, p_anyiadl_60p p_adl1_60p, p_adl2_60p, p_adl3p_60p))

  CV2_rename <- cd_CV2 %>% dplyr::rename('age' = a_age_60p,
                                        'cancre' = p_cancre_60p, 
                                        'diabe' = p_diabe_60p, 
                                        'hearte' = p_hearte_60p,
                                        'lunge' = p_lunge_60p,
                                        'smoken' = p_smoken_60p,
                                        'bmi' = a_bmi_60p,
                                        'employed' = p_employed_60p,
                                        'anyadl' = p_anyadl_60p)
                                        #'anyiadl' = p_anyiadl_60p)
                                        #'adl1' = p_adl1_60p,
                                        #'adl2' = p_adl2_60p,
                                        #'adl3p' = p_adl3p_60p)

  combine <- rbind(cd_l2, CV2_rename)

  melted <- reshape2::melt(combine, id.var = 'year', value.name = 'Prevalence')

  ggplot(data = melted, aes(x = year, y = Prevalence, color = variable)) +
          geom_line() +
          facet_wrap(. ~ variable, scales = "free")
          #theme(panel.spacing.x = unit(1.5, 'lines')) +
          #labs(title = 'Prevalence of Chronic Disease', x = 'Year', y = 'Prevalence')
}

# Load in whole stock pop, plus the CV2 summary output file
long <- read_dta('../../input_data/ELSA_long.dta')
CV2 <- read_dta('ELSA_CV2/ELSA_CV2_summary.dta')

vis_CV2_prev(long, CV2)
```

>>>>

```{r include=FALSE}
# Set up vector with all p-value column names. Require these for table formatting
pValNames <- c('P_Value_3', 'P_Value_4', 'P_Value_5', 'P_Value_6', 'P_Value_7', 'P_Value_8', 'P_Value_9')
```

@@

```{r echo = FALSE}
## This block will define the logic for creating the tables with Reactable
# The tables are formatted exactly the same for each group of vars so makes sense to define this only once

@@

### Binary Health
```{r echo = FALSE}
# Create the actual table!
binhlthTab <- createTTT(binhlth)
binhlthTab
```
### Binary Economic
```{r echo = FALSE}
# Create the actual table!
bineconTab <- createTTT(binecon)
bineconTab
```
### Count Economic
```{r echo = FALSE}
# Create the actual table!
cnteconTab <- createTTT(cntecon)
cnteconTab
```
### Risk Behaviours
```{r echo = FALSE}
# Create the actual table!
riskTab <- createTTT(risk)
riskTab
```
